My title

### 2024-12-02 paper/paper.qmd
updated download_data script to download data and updated cleaning to work with the new data + bugfixes
everything

https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=1810000402

@@

https://www150.statcan.gc.ca/n1/en/catalogue/81-582-X

>>>>

@@

https://data.ontario.ca/dataset/school-information-and-student-demographics/resource/e0e90bd5-d662-401a-a6d2-60d69ac89d14

https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=1810000501

https://stats.stackexchange.com/questions/11676/pseudo-r-squared-formula-for-glms
